Statistical Machine Learning Models on A Bank Marketing Dataset

### 2025-12-11 Slides.Rmd
EDA slides

---
title: "Statistical Machine Learning Models on A Bank Marketing Dataset"
author: "Sandra Afrifa, Tigist Kefelew, Mussa Hassen, Waddah Alaahtani"
subtitle: 'Colorado State University, DSCI 445: Statistical Machine Learning, Dr.Andee
  Kaplan'
output:
  ioslides_presentation:
    widescreen: true
---

@@

```{r slide2-plot, echo=FALSE, fig.align="center", out.width="75%"}
knitr::include_graphics("EDA/imbalance_plot.png")
```

@@

```{r eda1-plot, echo=FALSE, fig.align="center", out.width="75%"}
knitr::include_graphics("EDA/contact_plot.png")
```

@@

```{r eda2-plot, echo=FALSE, fig.align="center", out.width="68%"}
knitr::include_graphics("EDA/poutcome_plot.png")
```

@@

```{r eda3-plot, echo=FALSE, fig.align="center", out.width="75%"}
knitr::include_graphics("EDA/campaign_plot.png")
```

>>>>

---
title: "Statistical Machine Learning Models on A Bank Marketing Dataset"
author: "Sandra Afrifa, Tigist Kefelew, Mussa Hassen, Waddah Alqahtani"
subtitle: 'Colorado State University, DSCI 445: Statistical Machine Learning, Dr.Andee
  Kaplan'
output:
  ioslides_presentation:
    widescreen: true
---

@@

```{r imbalance-plot, echo=FALSE, fig.align="center", out.width="75%"}
ggplot(bank_full, aes(x = y, fill = y)) +
  geom_bar(color = "white") +
  scale_fill_manual(values = c("no" = "grey60", "yes" = "forestgreen")) +
  labs(
    title = "Distribution of Term Deposit Subscription",
    x = "Subscribed?",
    y = "Count"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")
```

@@

```{r contact-plot, echo=FALSE, fig.align="center", out.width="75%"}
ggplot(bank_full, aes(x = contact, fill = y)) +
  geom_bar(position = "fill", color = "white") +
  scale_fill_manual(values = c("no" = "grey60", "yes" = "forestgreen")) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Subscription Rate by Contact Method",
    x = "Contact Method",
    y = "Proportion (Yes)"
  ) +
  theme_minimal(base_size = 14)
```

@@

```{r poutcome-plot, echo=FALSE, fig.align="center", out.width="70%"}
ggplot(bank_full, aes(x = poutcome, fill = y)) +
  geom_bar(position = "fill", color = "white") +
  scale_fill_manual(values = c("no" = "grey60", "yes" = "forestgreen")) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Subscription Rate by Previous Outcome",
    x = "Previous Outcome",
    y = "Proportion (Yes)"
  ) +
  theme_minimal(base_size = 14)
```

@@

```{r campaign-plot, echo=FALSE, fig.align="center", out.width="75%"}
bank_full %>%
  group_by(campaign) %>%
  summarise(success_rate = mean(y == "yes")) %>%
  ggplot(aes(x = campaign, y = success_rate)) +
  geom_line(color = "steelblue", linewidth = 1.2) +
  geom_point(color = "darkorange", size = 3) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Success Rate vs. Number of Campaign Contacts",
    x = "Number of Contacts",
    y = "Success Rate"
  ) +
  theme_minimal(base_size = 14)
```
